Variability as a better characterization of Shannon entropy

### 2019-11-26 Articles/2019-ShannonEntropy/Submissions/AJP/AJP-ShannonEntropyIsVariability.tex
Title change
Adding Julian comments

\title{Universal Characterization of Physical Variability by \\Shannon's $-\sum_ip_i\,\textrm{ln}\,p_i$ Formula}

@@

%Cite Vlatko Vedral: Decoding Reality: The Universe as Quantum Information. Information is "the fundamental building block of the Universe".

%Cite Paul Davies Information and the Nature of Reality. Information "occupies the ontological basement"

%Cite Wheeler It from bit. "It is wrong, moreover, to regard this or that  physical quantity as sitting "out there" with this or that numerical value it is absorbed." "The information thus solicited make physics and comes in bits"

@@

In this paper we have seen that:
\begin{itemize}
	\item the Shannon entropy measures the variability of the elements within a given distribution, giving it a crisp intuitive meaning that is a general and applicable to all branches of science
	\item the expression is not arbitrary, as it is the only linear indicator for such concept
	\item it measures the variability by quantifying the number of yes/no questions one must ask to identify an element within the distribution, which corresponds to the number of bits needed to transmit or store that information
	\item when properly applied to statistical mechanics, the variability leads to the Boltzmann, Gibbs and von Neumann entropies.
\end{itemize}
The characterization we gave to the Shannon formula, then, is more precise than the common characterizations, such as disorder, information or lack of knowledge, and it should lead to less confusion. It clarifies that the Shannon variability is an independent concept from the entropy of thermodynamics and statistical mechanics, and a link can be recovered only if properly applied. We find that this approach, once internalized, gives greater intuitive insight and also maps more readily to the mathematical details.

>>>>

\title{Variability as a better characterization of Shannon entropy}

@@

@@

In this paper we have seen that:
\begin{itemize}
	\item the Shannon entropy measures the variability of the elements within a given distribution, giving it a crisp intuitive meaning that is general and applicable to all branches of science
	\item the expression is not arbitrary, as it is the only linear indicator for such a concept
	\item it measures the variability by quantifying the number of yes/no questions one must ask to identify an element within the distribution, which corresponds to the number of bits needed to transmit or store that information
	\item when properly applied to statistical mechanics, the variability leads to the Boltzmann, Gibbs and von Neumann entropies.
\end{itemize}
The characterization we gave to the Shannon formula, then, is more precise than the common characterizations, such as disorder, information or lack of knowledge, and it should lead to less confusion. It clarifies that the Shannon variability is an independent concept from the entropy of thermodynamics and statistical mechanics, and a link can be recovered only if properly applied. We find that this approach, once internalized, gives greater intuitive insight and also maps more readily to the mathematical details.
